---
title: "Final Project Phase I"
output: html_document
author: "Anna Liz Jensen, Maridol Guillen, Brooke Haley-Herevia, Keyur Joshi"
date: "January 29, 2022"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE, message = FALSE, warning = FALSE)
library(data.table)
library(readr)
# todo aj: don't forget to include other ext libs for knitr
```

### *Step 1*

We met as a group on a few occasions to settle on the data set we will describe in more detail in the next part of the document.

### *Step 2*

#### An intro to the data set

This data set...

#### Data source

This data set came from ....

#### Justification

We chose this particular data set because...

### *Step 3*

#### Import

```{r}
user_reviews_filename = "googleplaystore_user_reviews.csv"
play_store_ratings = "googleplaystore.csv"
user_reviews_df = fread(user_reviews_filename)
user_ratings_df = fread(play_store_ratings)
```

#### Listing Out Variables

```{r}
names(user_ratings_df)
names(user_reviews_df)
```

#### Structure

```{r}
str(user_ratings_df)
str(user_reviews_df)
```

#### Dimensions

```{r}
dim(user_ratings_df)
dim(user_reviews_df)
```

#### Head and Tail

```{r}
head(user_ratings_df)
head(user_reviews_df)

tail(user_ratings_df)
tail(user_reviews_df)
```

#### Missing Values

```{r}
length(which(is.na(user_ratings_df)))

length(which(is.na(user_reviews_df)))
```

#### Missing Values Per Column

```{r}


sapply(user_ratings_df, function(col) sum(is.na(col)))

sapply(user_reviews_df, function(col) sum(is.na(col)))
```

#### Summary of Cleaning Expectations

We expect to clean the follow aspects of the data

-   Remove NaN rows from consideration

-   Join the datasets together on the app name most likely

-   Parse and convert many character values to numeric (Android ver, size, installs etc)

    -   should also convert last updated to a datetime

    -   Type variable is a boolean -- we should change it to `isFree` and use logical values
