---
title: "Final Project Phase I"
output: html_document
author: "Anna Liz Jensen, Maridol Guillen, Brooke Haley-Herevia, Keyur Joshi"
date: "January 29, 2022"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE, message = FALSE, warning = FALSE)
library(data.table)
library(readr)
# todo aj: don't forget to include other ext libs for knitr
```

### *Step 1*

We met as a group on a few occasions to settle on the data set we will describe in more detail in the next part of the document.

### *Step 2*

#### An intro to the data set

This data set...

#### Data source

This data set came from ....

#### Justification

We chose this particular data set because...

### *Step 3*

#### Import

```{r}

```

#### Listing Out Variables

```{r}

```

#### Structure

```{r}

```

#### Dimensions

```{r}

```

#### Head and Tail

```{r}

```

#### Missing Values

```{r}

```

#### Missing Values Per Column

```{r}

```

#### Summary of Cleaning Expectations

We expect to clean the follow aspects of the data

-   aspect 1

-   aspect 2

-   aspect 3

-   etc.
